Network Analysis of Code Similarity

### 2014-11-21 network-analysis.Rmd
Get influences function

significance_threshold <- 0.15
cf2[cf2 < significance_threshold] <- NA
cf2[is.na(cf2)] <- 0
```

@@

```{r}
ny <- which(V(g)$name == "NY1850")
neighbors(g, ny)
graph.neighborhood(g, order = 2, nodes = ny)[[1]] %>%
  plot_graph()
```

>>>>

significance_threshold <- 0.03
cf2[cf2 < significance_threshold] <- NA
cf2[is.na(cf2)] <- 0
```

@@

```{r}
ny <- which(V(g)$name == "IA851")
neighbors(g, ny)
graph.neighborhood(g, order = 1, nodes = ny)[[1]] %>%
  plot_graph()
```

Get all the influences for people who need words.

```{r}
influences <- colnames(cf2) %>%
  lapply(., function(name) { get_influences(cf2, name, 10) })
names(influences) <- colnames(cf2)
print(influences)
```
